Figures for 3-D printed oxygen devices

### 2015-03-10 publishing/latex/plos_template.tex
working on discussion

This 3D-printed device improves on our previous design in a number of ways.
First, the fabrication is greatly simplified. 
No microfabrication, PDMS molding or Parylene coating is required.
3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the pipe within a pipe design. 
Moving forward with additive manufacturing of microfluidic devices is desirable. 
A comprable PDMS device would require several additional microfabriated layers to be manually aligned to reporduce just the distribution newtork.
Additionally, the non-premanat addheasion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
In PDMS devices the layers are bonded permantly via plasma bonding so damage to a membrane is not repairable.

>>>>

This 3D-printed device improves on our previous design in a number of ways.
First, the fabrication is greatly simplified. 
No microfabrication, PDMS molding or Parylene coating is required.
3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the 'pipe within a pipe' design. 
Moving forward with additive manufacturing of microfluidic devices is desirable. 
A comprable PDMS device would require several additional microfabriated layers to be manually aligned to reporduce just the distribution newtork.
Additionally, the non-premanat addheasion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
In PDMS devices the layers are bonded permantly via plasma bonding so damage to a membrane is not repairable.
